The Tail Risk Premium - Extension of Lottery Preference Premium

### 2025-03-04 paper.qmd
Added Charts To Paper

---
title: "The Tail Risk Premium - Extension of Lottery Preference Premium"
format: html

---
## Abstract
The investment strategy centered around the Idiosyncratic Volatility (IVOL) Risk Premium exploits the distinct performance patterns of stocks exhibiting varying levels of firm-specific risk. Unlike systemic risk, which permeates the entire market, idiosyncratic volatility is unique to individual firms and can be effectively diversified within a well-constructed portfolio. Empirical research consistently demonstrates that stocks with low idiosyncratic volatility tend to outperform those with high idiosyncratic volatility, suggesting a negative risk premium for high-IVOL stocks and a positive premium for low-IVOL stocks. This phenomenon has been validated across diverse international markets and controlled for market, size, and book-to-market factors, forming the foundation of this investment strategy.

@@

>>>>

---
title: "The Tail Risk Premium - Extension of Lottery Preference Premium"
author: "Brayden Boyko, Roan Henderson, Andrew Pettifor"
format:
  html:
    code_folding: hide
    self_contained: true
    toc: false
    dev: "png"
    fig_embed: true
    embed-resources: true
execute:
  echo: false
jupyter:
  kernel: python3
---
## Abstract
The investment strategy centered around the Idiosyncratic Volatility (IVOL) Risk Premium exploits the distinct performance patterns of stocks exhibiting varying levels of firm-specific risk. Unlike systemic risk, which permeates the entire market, idiosyncratic volatility is unique to individual firms and can be effectively diversified within a well-constructed portfolio. Empirical research consistently demonstrates that stocks with low idiosyncratic volatility tend to outperform those with high idiosyncratic volatility, suggesting a negative risk premium for high-IVOL stocks and a positive premium for low-IVOL stocks. This phenomenon has been validated across diverse international markets and controlled for market, size, and book-to-market factors, forming the foundation of this investment strategy.

@@

## Performance Evaluations
A variety of benchmark statistics will be included in our portfolio testing:

+ Annual / Monthly Return Values/Charts For 4 Portfolios
+ Description of Stock Breakdown For Four Portfolios (Skew, IVOL)
+ V1 & V2 Screening

### Monthly Returns

```{python}
from visuals import monthly_total_return

monthly_total_return()

```

#### Monthly Return Histogram
```{python}
from visuals import monthly_hist

monthly_hist()
```

#### Annual Returns

#### V1 Screen: High-Low IVOL

```{python}
from visuals import monthly_ivol

monthly_ivol()
```

#### V2 Screen: Negative-Positive Skew

#### V2 Alpha

```{python}
from visuals import monthly_alpha

monthly_alpha()

```
